G85R vs WT (M + F)

### 2023-09-13 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
update

##GO and KEGG Enrichment function

@@

data = data[20:1,]
data$Score = -log10(data$adjp)
data$term = factor(data$Name, levels = c(unique(data$Name)))

@@

##GR vs WT Females

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.FC"] <= .05]
bg1 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.FC"]<= 1]

@@

```{r include = F, echo = F}

GOID = "GO:0005634"
GenesInGO = genesingo[GOID]

GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInGO[[1]], "FBgn"]

@@

```{r include = F, echo = F}

ParentID = "GO:0044271"
GOIDs = row.names(reducedTerms)[reducedTerms$parent == ParentID]
GOID = GOIDs[1]
GenesInParent= unique(genesingo[[GOID]])
i=2
while(i<=length(GOIDs)){
  GOID = GOIDs[i]
  GenesInParent= unique(GenesInParent, genesingo[[GOID]])
  i=i+1
}

GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInParent, "FBgn"]

```{r echo =F, warnings = F}

comparison = "GRxWT.FC"
comparison2 = "GRxWT.MC"

hmdata = cpmdata[GenesInGO, groups$Group == "GR.F" | groups$Group == "WT.F"]
hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "GR.F" | groups$Group == "WT.F"]

hover.text = round(hmdata, digits = 1)

FDR = hmdata
FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]

FBgn = hmdata
FBgn[,1:ncol(FBgn)] = row.names(FBgn)

i=1
while(i<=ncol(hover.text)){
  hover.text[,i] = paste("CPM = ", hover.text[,i],
                         "\nFDR = ", FDR[,i],
                         "\nFBgn = ", FBgn[,i])
  i=i+1
}

hmdata2 = cpmdata[GenesInGO, groups$Group == "GR.M" | groups$Group == "WT.M"]
hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "GR.M" | groups$Group == "WT.M"]

hover.text2 = round(hmdata2, digits = 1)

FDR2 = hmdata2
FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]

FBgn2 = hmdata2
FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)

i=1
while(i<=ncol(hover.text2)){
  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
                         "\nFDR = ", FDR2[,i],
                         "\nFBgn = ", FBgn2[,i])
  i=i+1
}

hmdata = cbind(hmdata, hmdata2)
hover.text = cbind(hover.text, hover.text2)

heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            show_dendrogram = c(F,T),
            Rowv=T,
            Colv=T,
            ##cexRow = 1/(as.numeric(input$tophits)/25),
            na.color="grey",
            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
            ##cexCol = col.text,
            cexCol = 1,
            key = T,
            ##margins = c(50,350,NA,0),
            ##row_dend_left = T,
            column_text_angle = 90,

            ##col_side_colors=color.groups,
            ##col_side_palette=Spectral,
            ##main= "",
            custom_hovertext = hover.text)

##############
## GRxWT Df ##
##############

comparison1 = "GRxWT.FDf"
comparison2 = "GRxWT.MDf"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktDfGR.M" | groups$Group == "TktDfGR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

sigs = sigsKEY$Symbol

sig.cats = Enrichment(sigs)

```{r echo =F, warnings = F}

comparison = "GRxWT.FDf"
comparison2 = "GRxWT.MDf"

##hmdata = cpmdata[GenesInGO, groups$Group == "GR.F" | groups$Group == "WT.F"]
hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "GR.F" | groups$Group == "WT.F"]

hover.text = round(hmdata, digits = 1)

FDR = hmdata
FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]

FBgn = hmdata
FBgn[,1:ncol(FBgn)] = row.names(FBgn)

i=1
while(i<=ncol(hover.text)){
  hover.text[,i] = paste("CPM = ", hover.text[,i],
                         "\nFDR = ", FDR[,i],
                         "\nFBgn = ", FBgn[,i])
  i=i+1
}

##hmdata2 = cpmdata[GenesInGO, groups$Group == "GR.M" | groups$Group == "WT.M"]
hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "GR.M" | groups$Group == "WT.M"]

hover.text2 = round(hmdata2, digits = 1)

FDR2 = hmdata2
FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]

FBgn2 = hmdata2
FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)

i=1
while(i<=ncol(hover.text2)){
  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
                         "\nFDR = ", FDR2[,i],
                         "\nFBgn = ", FBgn2[,i])
  i=i+1
}

hmdata = cbind(hmdata, hmdata2)
hover.text = cbind(hover.text, hover.text2)

heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            show_dendrogram = c(F,T),
            Rowv=T,
            Colv=T,
            ##cexRow = 1/(as.numeric(input$tophits)/25),
            na.color="grey",
            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
            ##cexCol = col.text,
            cexCol = 1,
            key = T,
            ##margins = c(50,350,NA,0),
            ##row_dend_left = T,
            column_text_angle = 90,

            ##col_side_colors=color.groups,
            ##col_side_palette=Spectral,
            ##main= "",
            custom_hovertext = hover.text)

##############
## GRxWT OE ##
##############

comparison1 = "GRxWT.FOE"
comparison2 = "GRxWT.MOE"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktOEGR.M" | groups$Group == "TktOEGR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

sigs = sigsKEY$Symbol

sig.cats = Enrichment(sigs)

```{r include = F, echo = F}

GOID = "GO:0003723"
GenesInGO = genesingo[GOID]

GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInGO[[1]], "FBgn"]

```{r include = F, echo = F}
ParentID = "GO:0034249"
GOIDs = row.names(reducedTerms)[reducedTerms$parent == ParentID]
GOID = GOIDs[1]
GenesInParent= unique(genesingo[[GOID]])
i=2
while(i<=length(GOIDs)){
  GOID = GOIDs[i]
  GenesInParent= unique(GenesInParent, genesingo[[GOID]])
  i=i+1
}

GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInParent, "FBgn"]

```{r echo =F, warnings = F}

comparison = "GRxWT.FOE"
comparison2 = "GRxWT.MOE"

hmdata = cpmdata[GenesInGO, groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"]
hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"]

hover.text = round(hmdata, digits = 1)

FDR = hmdata
FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]

FBgn = hmdata
FBgn[,1:ncol(FBgn)] = row.names(FBgn)

i=1
while(i<=ncol(hover.text)){
  hover.text[,i] = paste("CPM = ", hover.text[,i],
                         "\nFDR = ", FDR[,i],
                         "\nFBgn = ", FBgn[,i])
  i=i+1
}

hmdata2 = cpmdata[GenesInGO, groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"]
hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"]

hover.text2 = round(hmdata2, digits = 1)

FDR2 = hmdata2
FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]

FBgn2 = hmdata2
FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)

i=1
while(i<=ncol(hover.text2)){
  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
                         "\nFDR = ", FDR2[,i],
                         "\nFBgn = ", FBgn2[,i])
  i=i+1
}

hmdata = cbind(hmdata, hmdata2)
hover.text = cbind(hover.text, hover.text2)

heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            show_dendrogram = c(F,T),
            Rowv=T,
            Colv=T,
            ##cexRow = 1/(as.numeric(input$tophits)/25),
            na.color="grey",
            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
            ##cexCol = col.text,
            cexCol = 1,
            key = T,
            ##margins = c(50,350,NA,0),
            ##row_dend_left = T,
            column_text_angle = 90,

            ##col_side_colors=color.groups,
            ##col_side_palette=Spectral,
            ##main= "",
            custom_hovertext = hover.text)

#########################
## Comparing the three ##
#########################

```{r include = F, echo = F}

comparison1 = "GRxWT.FC"
comparison2 = "GRxWT.MC"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "GR.F" | groups$Group == "WT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "GR.M" | groups$Group == "GR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

C.sigs = sigsKEY$Symbol

comparison1 = "GRxWT.FDf"
comparison2 = "GRxWT.MDf"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktDfGR.M" | groups$Group == "TktDfGR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

Df.sigs = sigsKEY$Symbol

comparison1 = "GRxWT.FOE"
comparison2 = "GRxWT.MOE"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktOEGR.M" | groups$Group == "TktOEGR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

OE.sigs = sigsKEY$Symbol

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Control"
set2="Defficient"
set3="Over Expression"
##set4="GSC2.Stem"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = C.sigs
s2 = Df.sigs
s3 = OE.sigs
##s4=row.names(temp)[temp[,4]==1]

data = data.frame(Condition = c("Control", "Defficient", "Over Expression"), DEGs = c(length(C.sigs), length(Df.sigs), length(OE.sigs)))

fig <- plot_ly(data, 
               x = ~Condition, y = ~DEGs, 
               type = 'bar',
               name = ~Condition,
               color = ~Condition,
               colors = c("coral3","gold2", "steelblue3"),
               marker = list(line = list(color = "black", width = 1.5)))

@@

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("brown1","gold2", "steelblue2"),cex=1.5,cat.cex = 1)

@@

>>>>

##GO and KEGG Enrichment function
```{r echo = F, include = F}

@@

data$term = data$Name
if(length(unique(data$term)) < length(data$term)){
  data$term[duplicated(data$term)] = paste(data$term[duplicated(data$term)], "2")
}  
data = data[20:1,]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

@@

##GR vs WT Females
sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.FC"] <= .05]
bg1 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.FC"]<= 1]

@@

##GR.F vs WT.F specific volcano

specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go')

specific.cat = specific.cat[2]
parent.category = 'neurogenesis'
specific.kegg = "DNA replication"
specific.go =  '32553'

set.size = F

GOterm.genes = vector('list', length = length(unique(reducedTerms$parent)))
names(GOterm.genes) = unique(reducedTerms$parent)
i=1
while(i<=length(GOterm.genes)){
  goinparent = reducedTerms[grep(names(GOterm.genes)[i], reducedTerms$parent),'go']
  genesinparent = unlist(genesingo[goinparent])
  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
  i = i +1
}

volcano.data = data.frame(Symbol = GeneIDKey[row.names(TKT.EdgeR), "Symbol"], 
                          FDR = -log2(TKT.EdgeR[, 'GRxWT.FC']),
                          FC = TKT.EdgeR.FC[row.names(TKT.EdgeR), 'GRxWT.FC'],
                          ##Color = 0)
                          Color = 'grey',
                          size = 5*log(mean.cpm[row.names(TKT.EdgeR),"GR.F"]),
                          GR.F.cpm = mean.cpm[row.names(TKT.EdgeR),"GR.F"],
                          WT.F.cpm = mean.cpm[row.names(TKT.EdgeR),"WT.F"],
                          GO.terms = "none")

main.title = "Significant DEG in G85R Females vs. WT Females"

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

if(set.size == T){
  volcano.data$size = 15
  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
}

if(specific.cat == 'parent.category'){
  parent.genes = GOterm.genes[[intersect(reducedTerms[reducedTerms$parentTerm == parent.category, "go"], names(GOterm.genes))]]
  volcano.data$Color = 'honeydew'
  volcano.data[parent.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
}

if(specific.cat == 'specific.kegg'){
  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
  kegg.genes = names(kegg[grep(kegg.id, kegg)])
  volcano.data$Color = 'honeydew'
  row.names(volcano.data) = volcano.data$Symbol
    volcano.data[kegg.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
}

if(specific.cat == 'specific.go'){
  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
  volcano.data$Color = 'honeydew'
  go.genes = genesingo[[go.id]]
  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
  go.genes = intersect(go.genes, row.names(volcano.data))
  volcano.data[go.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
}

##volcano.data

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nFC: ", round(volcano.data$FC,2),
                      "\nG85R mean cpm: ", round(volcano.data$GR.F.cpm, 1),
                      "\nWT mean cpm: ", round(volcano.data$WT.F.cpm, 1)))
fig = fig %>% layout(title = main.title)

              ##color = ~Color,
              ##colors = 'Spectral')
              ##color = ~Color,
              ##colors = ~Color)
              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))

@@

```{r}
specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go')

specific.cat = specific.cat[1]
parent.category = 'chromosome organization'
specific.kegg = "DNA replication"
specific.go =  '006457'

set.size = F

GOterm.genes = vector('list', length = length(unique(reducedTerms$parent)))
names(GOterm.genes) = unique(reducedTerms$parent)
i=1
while(i<=length(GOterm.genes)){
  goinparent = reducedTerms[grep(names(GOterm.genes)[i], reducedTerms$parent),'go']
  genesinparent = unlist(genesingo[goinparent])
  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
  i = i +1
}

volcano.data = data.frame(Symbol = GeneIDKey[row.names(TKT.EdgeR), "Symbol"], 
                          FDR = -log2(TKT.EdgeR[, 'GRxWT.MC']),
                          FC = TKT.EdgeR.FC[row.names(TKT.EdgeR), 'GRxWT.MC'],
                          ##Color = 0)
                          Color = 'grey',
                          size = 5*log(mean.cpm[row.names(TKT.EdgeR),"GR.M"]),
                          GR.F.cpm = mean.cpm[row.names(TKT.EdgeR),"GR.M"],
                          WT.F.cpm = mean.cpm[row.names(TKT.EdgeR),"WT.M"],
                          GO.terms = "none")

main.title = "Significant DEG in G85R Males vs. WT Males"

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

if(set.size == T){
  volcano.data$size = 15
  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
}

if(specific.cat == 'parent.category'){
  parent.genes = GOterm.genes[[intersect(reducedTerms[reducedTerms$parentTerm == parent.category, "go"], names(GOterm.genes))]]
  volcano.data$Color = 'honeydew'
  volcano.data[parent.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
}

if(specific.cat == 'specific.kegg'){
  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
  kegg.genes = names(kegg[grep(kegg.id, kegg)])
  volcano.data$Color = 'honeydew'
  row.names(volcano.data) = volcano.data$Symbol
    volcano.data[kegg.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
}

if(specific.cat == 'specific.go'){
  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
  volcano.data$Color = 'honeydew'
  go.genes = genesingo[[go.id]]
  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
  go.genes = intersect(go.genes, row.names(volcano.data))
  volcano.data[go.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
}

##volcano.data

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nFC: ", round(volcano.data$FC,2),
                      "\nG85R mean cpm: ", round(volcano.data$GR.F.cpm, 1),
                      "\nWT mean cpm: ", round(volcano.data$WT.F.cpm, 1)))
fig = fig %>% layout(title = main.title)

@@

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)

KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))

metadata = data.frame(Sample = colnames(rawdata), 
                      Group = as.character(rawdata[1,]), 
                      TIC = as.numeric(rawdata[2,]), 
                      Genotypes = genotypes[as.character(rawdata[1,])])

norm.func = function(data){
  nd = (as.numeric(data)/metadata$TIC)*1000
  return(nd)
}

norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
colnames(norm.data) = colnames(rawdata)

group.mean=function(data){
  gm = mean(na.omit(data))
}

mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
row.names(mean.data) = row.names(norm.data)
colnames(mean.data) = unique(metadata$Group)

i=1
while(i<=ncol(mean.data)){
  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
  i = i+1
}

compare.conditions = function(condition1, condition2){
  columns1 = metadata[metadata$Group == condition1, "Sample"]
  columns2 = metadata[metadata$Group == condition2, "Sample"]
  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
  i=1
  while(i<=length(p)){
    if(length(na.omit(norm.data[i,columns1]))>2 & 
       length(na.omit(norm.data[i,columns2]))>2){
      temp = t.test(na.omit(norm.data[i,columns1]),
                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
      p[i] = temp[[3]]
      }
    i=i+1
    }

  fdr = p.adjust(p, "BH", length(p))

  fc = mean.data[,condition1]/mean.data[,condition2]

  comparison.table = data.frame(p = p, 
                                FDR = fdr, 
                                FC = fc, 
                                KEGG = KEGG.Key[row.names(mean.data)])

  comparison.table = comparison.table[order(comparison.table$FDR),]
}
d
GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")
GRxWT.OE = compare.conditions("F", "A")

@@

set.size == F
volcano.data = data.frame(Symbol = row.names(GRxWT.C), 
                          FDR = -log2(GRxWT.C$FDR),
                          FC = log2(GRxWT.C$FC),
                          Color = 'honeydew',
                          size = log(mean.data[row.names(GRxWT.C),'E']),
                          GR.Level = mean.data[row.names(GRxWT.C), "E"],
                          WT.Level = mean.data[row.names(GRxWT.C), "C"],
                          GO.terms = "none")

main.title = "Metabolites in G85R Males vs. WT Males"

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

##volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

if(set.size == T){
  volcano.data$size = 15
  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
}

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Metabolite:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nFC: ", round(volcano.data$FC,2),
                      "\nG85R mean cpm: ", round(volcano.data$GR.Level, 1),
                      "\nWT mean cpm: ", round(volcano.data$WT.Level, 1)))
fig = fig %>% layout(title = main.title)

```{r, include = F, echo = F}

if(intersect(list.files(), "KEGG_Image_Files") != "KEGG_Image_Files"){
  dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
}

Home = dirname(rstudioapi::getSourceEditorContext()$path)
OutputDir = paste0(Home, "/KEGG_Image_Files/")

ShowKEGG = function(PathwayID){

download.kegg(pathway.id= PathwayID, species = "dme", kegg.dir = OutputDir)
xml.file=paste0(OutputDir, "dme",PathwayID,".xml")
node.data=node.info(xml.file)

all.path = names(kegg[grep(PathwayID,kegg)])

up = TKT.EdgeR.FC[TKT.EdgeR.FC$Moderate == 1, "Symbol"]
Moderate = intersect(Moderate, all.path)
Moderate = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Moderate, "CG"],sep="")

Strong = Df.data[Df.data$Strong == 1, "Symbol"]
Strong = intersect(Strong, all.path)
Strong = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")

Enhancer = Df.data[Df.data$Enhancer == 1, "Symbol"]
Enhancer = intersect(Enhancer, all.path)
Enhancer = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Enhancer, "CG"],sep="")

Lethal = Df.data[Df.data$Lethal == 1, "Symbol"]
Lethal = intersect(Lethal, all.path)
Lethal = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")

plot.data.gene=node.map(mol.data=c(Moderate, Strong, Enhancer, Lethal), node.data, node.types="gene")
cols.ts.gene = node.color(plot.data.gene, limit=2, bins=2)
cols.ts.gene[1:length(cols.ts.gene)] = 0

pdg.moderate=node.map(mol.data=Moderate, node.data, node.types="gene")
temp = node.color(pdg.moderate, limit=2, bins=2)
ctg.moderate = cols.ts.gene
ctg.moderate[temp!="#FFFFFF"]= 1 ##"gold2"

pdg.strong=node.map(mol.data=Strong, node.data, node.types="gene")
temp = node.color(pdg.strong, limit=2, bins=2)
ctg.strong = cols.ts.gene
ctg.strong[temp!="#FFFFFF"]= 1 ##"brown2"

pdg.enhancer=node.map(mol.data=Enhancer, node.data, node.types="gene")
temp = node.color(pdg.enhancer, limit=2, bins=2)
ctg.enhancer = cols.ts.gene
ctg.enhancer[temp!="#FFFFFF"]= 1 ##"deepskyblue"

pdg.lethal=node.map(mol.data=Lethal, node.data, node.types="gene")
temp = node.color(pdg.lethal, limit=2, bins=2)
ctg.lethal = cols.ts.gene
ctg.lethal[temp!="#FFFFFF"]= 1 ##"navyblue"

color.combos = data.frame(Moderate = as.numeric(ctg.moderate),
                          Strong = as.numeric(ctg.strong),
                          Enhancer = as.numeric(ctg.enhancer),
                          Lethal = as.numeric(ctg.lethal))
row.names(color.combos)= names(cols.ts.gene)

cols.ts.gene[cols.ts.gene=="0"]="darkseagreen1"

cols.ts.gene[row.names(color.combos)[color.combos$Moderate == 1]] = "gold2"
cols.ts.gene[row.names(color.combos)[color.combos$Strong   == 1]] = "brown1"
cols.ts.gene[row.names(color.combos)[color.combos$Enhancer   == 1]] = "lightsteelblue"
cols.ts.gene[row.names(color.combos)[color.combos$Lethal   == 1]] = "cornflowerblue"
cols.ts.gene[row.names(color.combos)[(color.combos$Moderate   == 1 | color.combos$Strong   == 1) & (color.combos$Enhancer   == 1 | color.combos$Lethal   == 1) ]] = "grey60"

setwd(OutputDir)
pv.pars= keggview.native(plot.data.gene=plot.data.gene,
                         cols.ts.gene=cols.ts.gene, 
                         node.data=node.data,
                         pathway.name=paste0("dme", PathwayID),
                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1],
                         kegg.dir = OutputDir)
setwd(Home)
}

PathwayID = "04150"

ShowKEGG(PathwayID)

```{r echo = F, fig.align='center'}

knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
